*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-05 Code/Manuscript_O2.Rmd
caption wording

LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
                      "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",

@@

knitr::kable(MaxGrowthTable,
             caption = "The maximum growth rate, µ~max~ (d^-1^) in each O~2~ experiment for each strain. The corresponding photoperiod, PAR level and spectral waveband are indicated.",
            col.names =  c("Strain",
                          "Photoperiod (h)",
                          "PAR (µmol photons m^-2^ s^-1^)",
                          "Spectral waveband (nm)",
                          "[O~2~] (µM)",
                          "µ~max~ (d^-1^)"),
              align = "lccccc"
             )
```

@@

To Be Entered through PLoSONe system and deleted here
Czech Academy of Science visiting fellowship supporting DAC work at AlgaTech (OP)
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)

>>>>

LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
                      "Spectral waveband, light level and photoperiod are individually controlled for each culture tube.",
                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of cultures.",
                      "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",

@@

knitr::kable(MaxGrowthTable,
             caption = "The maximum growth rate, µ~max~ (d^-1^) achieved for each O~2~ experiment, for each strain, with the corresponding photoperiod, PAR level and spectral waveband.",
            col.names =  c("Strain",
                          "Photoperiod (h)",
                          "PAR (µmol photons m^-2^ s^-1^)",
                          "Spectral waveband (nm)",
                          "[O~2~] (µM)",
                          "µ~max~ (d^-1^)"),
              align = "lccccc"
             )
```

@@

To Be Entered through PLoSONe system and deleted here
Czech Academy of Science (OP) visiting fellowship supporting DAC work at AlgaTech
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)
